Whole-genome pairwise alignment using the hierarchical wavefront algorithm

### 2022-04-01 manuscript/main.tex
typo

\address{
$^{\text{\sf 1}}$Genomics Research Centre, Human Technopole, Viale Rita Levi‑Montalcini 1, Milan, 20157, Italy \\
$^{\text{\sf 2}}$Department of Computer Sciences, University of Pisa, Pisa, 56127, Italy \\
$^{\text{\sf 3}}$Department of Computer Sciences, Barcelona Supercomputing Center, Barcelona, 08034, Spain \\
$^{\text{\sf 4}}$Departament d’Arquitectura de Computadors i Sistemes Operatius, Universitat Autònoma de Barcelona, Barcelona, 08193, Spain \\
$^{\text{\sf 5}}$Department of Genetics, Genomics and Informatics, University of Tennessee Health Science Center, Memphis, 38163, Tennessee, USA
}

>>>>

\address{
$^{\text{\sf 1}}$Genomics Research Centre, Human Technopole, Viale Rita Levi‑Montalcini 1, Milan, 20157, Italy \\
$^{\text{\sf 2}}$Department of Computer Sciences, University of Pisa, Pisa, 56127, Italy \\
$^{\text{\sf 3}}$Department of Computer Sciences, Barcelona Supercomputing Center, Barcelona, 08034, Spain \\
$^{\text{\sf 4}}$Department d’Arquitectura de Computadors i Sistemes Operatius, Universitat Autònoma de Barcelona, Barcelona, 08193, Spain \\
$^{\text{\sf 5}}$Department of Genetics, Genomics and Informatics, University of Tennessee Health Science Center, Memphis, 38163, Tennessee, USA
}
